Equalizer\\Programming and User Guide

### 2010-10-04 Developer/ProgrammingGuide/paper.tex
Programming Guide: minor update
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.8 for Equalizer 0.9.1+svn\\[\medskipamount]
%  \today
}

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_AFFINITY\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\textbar \ EXTERN\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines how the window handles the affinity context (WGL
  only). This hint is a workaround for NVidia drivers greater than 200, which
  contain a faulty implementation of the WGL\_NV\_gpu\_affinity extension. When
  set to AUTO, the hint is interpreted like EXTERN for windows and pbuffers with
  these drivers, in all other cases it is interpreted like ON. When set to ON,
  an affinity DC is used for all drawable types. When set to EXTERN, a normal DC
  is used to create the drawable, but an affinity DC is created and can be used
  by the application to render into a FBO. This hint may be ignored in later
  versions of Equalizer, once this workaround has become obsolete.\\
\end{tabularx}\\\vfill

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CHANNEL\_IATTR\_HINT\_STATISTICS\\
  \textbf{Value} & OFF \textbar \ FASTEST [ ON ] \textbar \ NICEST\\
  \textbf{Default} & FASTEST [Release Build]\\
                   & NICEST [Debug Build]\\
  \textbf{Details} & See EQ\_WINDOW\_IATTR\_HINT\_STATISTICS.\\
  \textbf{See also} & EQ\_NODE\_IATTR\_HINT\_STATISTICS 
  EQ\_WINDOW\_IATTR\_HINT\_STATISTICS\\
  \hline
\end{tabularx}\\%\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
  \textbf{Value} & QUAD \textbar \ ANAGLYPH\\
  \textbf{Default} & QUAD\\
  \textbf{Details} & Selects the algorithm used for stereo
  rendering. QUAD-buffered stereo uses the left and right buffers of a
  stereo window (active stereo). Anaglyphic stereo uses
  \textsf{glColorMask} to mask colors for individual eye passes, used in
  conjunction with colored glasses.\\
  \hline
\end{tabularx}\\%\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
  \textbf{Value} & [ RED GREEN BLUE ]\\
  \textbf{Default} & [ RED ] \\
  \textbf{Details} & Select the color mask for the left eye pass during
  anaglyphic stereo rendering.\\
  \hline
\end{tabularx}\\%\vfill

@@

    attributes
    {
        stereo_mode                  QUAD | ANAGLYPH    # default QUAD
        stereo_anaglyph_left_mask    [ RED GREEN BLUE ] # default red
        stereo_anaglyph_right_mask   [ RED GREEN BLUE ] # df green blue
    }

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.8 for Equalizer 0.9.1+svn\\[\medskipamount]
%  \today
}

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_AFFINITY\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\textbar \ EXTERN\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines how the window handles the affinity context (WGL
  only). This hint is a workaround for NVidia drivers greater than 200, which
  contain a faulty implementation of the WGL\_NV\_gpu\_affinity extension. When
  set to AUTO, the hint is interpreted like EXTERN for windows and pbuffers with
  these drivers, in all other cases it is interpreted like ON. When set to ON,
  an affinity DC is used for all drawable types. When set to EXTERN, a normal DC
  is used to create the drawable, but an affinity DC is created and can be used
  by the application to render into a FBO. This hint may be ignored in later
  versions of Equalizer, once this workaround has become obsolete.\\
  \hline
\end{tabularx}\\\vfill

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CHANNEL\_IATTR\_HINT\_STATISTICS\\
  \textbf{Value} & OFF \textbar \ FASTEST [ ON ] \textbar \ NICEST\\
  \textbf{Default} & FASTEST [Release Build]\\
                   & NICEST [Debug Build]\\
  \textbf{Details} & See EQ\_WINDOW\_IATTR\_HINT\_STATISTICS.\\
  \textbf{See also} & EQ\_NODE\_IATTR\_HINT\_STATISTICS 
  EQ\_WINDOW\_IATTR\_HINT\_STATISTICS\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
  \textbf{Value} & AUTO \textbar QUAD \textbar \ ANAGLYPH\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Selects the algorithm used for stereo
  rendering. QUAD-buffered stereo uses the left and right buffers of a
  stereo window (active stereo). Anaglyphic stereo uses
  \textsf{glColorMask} to mask colors for individual eye passes, used in
  conjunction with colored glasses. AUTO selects QUAD if the drawable is capable
  of active stereo rendering, otherwise ANAGLYPH is selected\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
  \textbf{Value} & [ RED GREEN BLUE ]\\
  \textbf{Default} & [ RED ] \\
  \textbf{Details} & Select the color mask for the left eye pass during
  anaglyphic stereo rendering.\\
  \hline
\end{tabularx}\\\vfill

@@

    attributes
    {
        stereo_mode                  AUTO | QUAD | ANAGLYPH    # default AUTO
        stereo_anaglyph_left_mask    [ RED GREEN BLUE ] # default red
        stereo_anaglyph_right_mask   [ RED GREEN BLUE ] # df green blue
    }
